---
title: "Simulation about POR and PR"
author: "Boyi Guo"
date: "1/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
```

# POR vs PR
POR stands for prevalence odds ratio, while PR stands for Prevalence ratio. 

# Why not OR and RR

# Population POR,PR vs Sample POR,PR


# Empirical evaluation of OR, RR approximation

The objective of this simulation is to see, when the prevalence is how small, the odds ratio is not a good approximation of risk ratio.

The factor we control is
* Confonder: No confonder, i.e. no covariates to adjust for
* Risk ratio: we control the magnitude of risk ratio
* Study design: Two arms, balanced i.e. case to control ratio is 1
* sample size (per group): 50
* Prevalence of the oucome of interest
*


```{r}
n.it <- 1000

# per-group sample size
n <- 50

# Prevalence of the outcome, i.e. how rare is the disease
prev <- (1:99)/100

# Population POR
or <- 2

p.control <- prev[20]


c <- or * p.control/(1-p.control)

p.case <- c/(1+c)

tmp <- map_dbl(1:n.it, .f = function(x){
  set.seed(x)
  treat <- rep(c("control", "case"), each=n) %>% 
    factor(levels = c("control","case"))
  control.dis <- rbinom(n, size = 1, prob = p.control)
  case.dis <- rbinom(n, size=1, prob = p.case)
  outcome <- factor(c(control.dis, case.dis))
  
  log.mdl <- glm(outcome~treat, family = binomial)
  coef(log.mdl)[2] %>% exp
})

mean(tmp)

```

# Defining Rare
